Combined Task and Motion Planner through an Interface Layer

### 2015-05-12 documentation/ps4.tex
now compiles with url
minor changes
added motion planner heuristic

\usepackage{fancyhdr} % Required for custom headers
\usepackage{float}
\usepackage{lastpage} % Required to determine the last page for the footer
\usepackage{extramarks} % Required for headers and footers
\usepackage{graphicx} % Required to insert images
\usepackage{amssymb}
\usepackage{enumerate}
\usepackage{svg}
\usepackage{caption}
\usepackage{subfig}

@@

@@

\subsection{Sorting}
We ran the sorting task in simulation and on the physical Baxter robot.
The planner took approximately an hour to find a feasible plan. 
We ran many test trials to achieve a successful run because the system was open-loop with respect to the environment.
It had feedback on the world position of the arms, but not on the position of the arms relative to the objects. This mean that drift accumulated over time.
Baxter successfully sorts green, red, and blue blocks into different bins. 
A video of the successful test trial can be found at http://youtu.be/445_t_lUBdU.
\begin{figure}
\begin{tabular}[t]{|l|l|l|l|l|l|l|}
\hline

>>>>

\usepackage{fancyhdr} % Required for custom headers
\usepackage{float}
\usepackage{lastpage} % Required to determine the last page for the footer
\usepackage{extramarks} % Required for headers and footers
\usepackage{graphicx} % Required to insert images
\usepackage{amssymb}
\usepackage{enumerate}
\usepackage{svg}
\usepackage{hyperref}
\usepackage{caption}
\usepackage{subfig}

@@

We added a heuristic to avoid motion planner calls in cases where we could easily determine that it would fail.
Specifically, the motion planner service would use the world geometry and basic collision geometry to determine if the pose obviously would cause the robot arm to intersect with obstacles.
This greatly increased the efficiency for planning in crowded environments since it enabled the motion planner to return a fail much more quickly, rather than trying the full planning procedure when the end goal wasn't reachable.

@@

\subsection{Sorting}
We ran the sorting task in simulation and on the physical Baxter robot.
The planner took approximately an hour to find a feasible plan. 
We ran many test trials to achieve a successful run because the system was open-loop with respect to the environment.
It had feedback on the world position of the arms, but not on the position of the arms relative to the objects. This mean that drift accumulated over time.
Baxter successfully sorts green, red, and blue blocks into different bins. 
A video of the successful test trial can be found at \url{http://youtu.be/445_t_lUBdU}.

\begin{figure}
\begin{tabular}[t]{|l|l|l|l|l|l|l|}
\hline
